Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
premier dessins SimpleProt

@@

  \centerline{
   \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
   \hspace{0.5cm}
   \includegraphics[width=4cm]{XFIG/FaultyMedium}
   }
   \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}

  %\end{minipage}
  \vspace{1cm}
%\begin{minipage}{6cm}
  \centerline{\includegraphics[width=11cm]{XFIG/ABP4-Schema}}
  \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
%\end{minipage}

@@

Fig. \ref{ABP:Schema} shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying network is modelled by two media,
carrying the message together with a control bit on one way, and an
acknowledge back from $receiver$ to $sender$. The media can be perfect (safe), or
faulty (losing or duplicating messages) as shown in
Fig. \ref{schema:ABP-media}. Remark that the pLTSs shown in
Fig. \ref{schema:ABP-media} are in fact ``generic'' in the sense that
they will be instanciated in different ways depending on the number
and types of the message arguments. This is only a graphical syntax,
with an obvious semantics for building the corresponding pNets.

@@

>>>>

\begin{figure}[t]
  \centerline{
   \includegraphics[width=8cm]{XFIG/SimpleProt-Schema}
   }
   \caption{Schema of the Simple Protocol Example}  \label{SimpleProt:Schema}
\end{figure}

@@

  %% \centerline{
  %%  \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
  %%  \hspace{0.5cm}
  %%  \includegraphics[width=4cm]{XFIG/FaultyMedium}
  %%  }
  %%  \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}

  %\end{minipage}
%  \vspace{1cm}
%\begin{minipage}{6cm}
  \centerline{\includegraphics[width=11cm]{XFIG/SimpleProt-pNet}}
  \caption{Composed pNet with the Simple Protocol}  \label{schema:SimpleProt-composed}
%\end{minipage}

@@

Fig. \ref{SimpleProt:Schema} shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying network is modelled by two media,
carrying the message together with a control bit on one way, and an
acknowledge back from $receiver$ to $sender$. The media can be perfect (safe), or
faulty (losing or duplicating messages) as shown in
Fig. \ref{schema:ABP-media}. Remark that the pLTSs shown in
Fig. \ref{schema:ABP-media} are in fact ``generic'' in the sense that
they will be instanciated in different ways depending on the number
and types of the message arguments. This is only a graphical syntax,
with an obvious semantics for building the corresponding pNets.

@@

\section{ABP}
I have collected here all previous items about ABP, in case we wnat to
reuse them later
